An Authoritative Adventure

### 2020-12-22 article.tex
Added example table stuff and complex theme color settings stuff to article.tex

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{graphicx}
\usepackage{titling}

@@

% The settings below are an example of how to modify all of the theme colors.
% Note that the paper (\SetPaperImage) and footerscroll.pdf will probably need
% to be modified for any % major color scheme change. The values below are
% thematic for a sourcebook like GoS.
\definecolor {mytheme}      {HTML} {DCF1E5} %
\definecolor {mysidebar}    {HTML} {E9F5F5} %
\definecolor {myreadaloud}  {HTML} {DCF1E5} %
\definecolor {myreadaloudborder}  {HTML} {8AA7A2} %
\definecolor {mypagenum}  {HTML} {B5D4CF} %
%\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]

@@

\subsection{Tables}
The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\begin{lstlisting}
\begin{DndTable}[cX][PhbLightCyan]
  \textbf{d8} & \textbf{Item} \\
  1           & Small wooden button \\
  2           & Red feather \\
  3           & Human tooth \\
  4           & Vial of green liquid \\
  6           & Tasty biscuit \\
  7           & Broken axe handle \\
  8           & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

@@

\begin{lstlisting}
\begingroup
\DndSetThemeColor[PhbMauve]

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{graphicx}
\usepackage{titling}
\usetikzlibrary{intersections} % Required for ornamentedtabular

@@

% The settings below are an example of how to modify all of the theme colors.
% Note that the paper (\SetPaperImage) and footerscroll.pdf will probably need
% to be modified for any major color scheme change. The values below are
% thematic for a sourcebook like GoS.
\definecolor {mytheme}      {HTML} {DCF1E5} %
\definecolor {mysidebar}    {HTML} {E9F5F5} %
\definecolor {myreadaloud}  {HTML} {DCF1E5} %
\definecolor {myreadaloudborder}  {HTML} {8AA7A2} %
\definecolor {mypagenum}  {HTML} {B5D4CF} %
%\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]

@@

\section{Tables}

\subsection{Regular Table}

The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{DndTable}[cX][PhbLightCyan]
  \textbf{d8} & \textbf{Item} \\
  1           & Small wooden button \\
  2           & Red feather \\
  3           & Human tooth \\
  4           & Vial of green liquid \\
  6           & Tasty biscuit \\
  7           & Broken axe handle \\
  8           & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

@@

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begingroup
\DndSetThemeColor[PhbMauve]

@@

\subsection{More Theme Colors Control}
Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class. This command takes seven (7) |<color>| values that map to the following color variables within the theme:

\begin{DndTable}[header=Complex Theme Parameter Map]{cX}
  \textbf{Param \#} & \textbf{Variable Mapping} \\
  1 & \textit{themecolor}, \textit{tablecolor} \\
  2 & \textit{commentcolor}, \textit{sidebarcolor} \\
  3 & \textit{readaloudcolor} (DndReadAloud background) \\
  4 & \textit{readaloudbordercolor} \\
  5 & \textit{titlecolor} \\
  6 & \textit{titlerulecolor} \\
  7 & \textit{pagecolor} (page numbers and footer) \\
\end{DndTable}

\begin{DndComment}{Note On Changing Schemes}
If a major color scheme change is attempted, it is
likely that the background ``paper'' (which can be overridden with
|\SetPaperImage|) and footerscroll.pdf will need
to be modified as well in order to fit the other color modifications.
\end{DndComment}

An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook:

\begin{lstlisting}[basicstyle=\ttfamily\small]
\definecolor {mytheme} {HTML} {DCF1E5}
\definecolor {mysidebar} {HTML} {E9F5F5}
\definecolor {myreadaloud} {HTML} {DCF1E5}
\definecolor {myreadaloudborder} {HTML} {8AA7A2}
\definecolor {mypagenum} {HTML} {B5D4CF}
\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
\end{lstlisting}
